---
title: "multimix-introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{multimix-introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, we must install the package from github and load it into the environment 
```{r setup}
# install.packages("devtools") 
# devtools::install_github("michelleUMD/multimix")
library(multimix)
```

We have included a sample dataset for your convenience. The columns required are `Subject_ID`, `Time`, and  `Binary_outcome`
```{r}
data(sample_data)
head(sample_data)
```

To call the model, we use the `multimix` function. Because the model does not have an empirical solution, it uses an optimizer with by 20 random initial parameter guesses (default). You can keep the first plausible solution (`return_first_sucess = TRUE`) or exhaust all 20 tries to find the best one. You can also specify the number of guesses and the bounds for the guesses using arguments in this function. 
```{r}
mm_model <- multimix(
  df_long = sample_data, 
  return_first_sucess = TRUE
)
```

We can view the model parameters by calling `print()`
```{r}
print(mm_model)
```

We can visualize the model by calling `plot()`
```{r}
plot(mm_model)
```

